
\documentclass[10pt]{article}

\title{CS423 Summary: Hints for computer system design}
\author{Hongpeng Guo}
\date{\today}
\begin{document}
\maketitle

\noindent
{\bf Area:}

This paper provides the general hints or anecdotes in system design. The Area fits generally in the whole designing of operating system.
\\

\noindent
{\bf Problem:}

This paper did not work on a specific problem in system design area, but it provided a list of advice for system designers. 
\\

\noindent
{\bf Methodology:}

In order to reasonably provide suggestions. The author of this paper carefully provide logical reasoning and real-world example to answer two questions for every tip. These questions are:
\begin{itemize}
\item
Why it helps in making a good system.
\item
Where in the system design it helps.
\end{itemize}

\noindent
{\bf Solution:}

The solution are the list of tips categorized into three areas
\begin{itemize}
\item
Functionality:
\begin{itemize}
\item 
The tips include: keep it simple; make it fast; don't hide power; use procedure arguments ... etc.
\end{itemize}

\item
Speed:
\begin{itemize}
\item
The tips include: split resources; use static analysis; dynamic translation; cache answer; ...etc.
\end{itemize}

\item
Fault-tolerate:
\begin{itemize}
\item 
The tips include: end to end monitoring and log update.
\end{itemize}
\end{itemize}
\noindent
{\bf Results:}

As this paper did not work on a specific problem. There is no metric to evaluate the result. But these hints are really helpful for a system designer from today's point of view.
\\

\noindent
{\bf Takeaway:}

This paper is made up of takeaway suggestions. Any system builder should pay attention to these hints.

\end{document}
